### 2024-10-09 esop25/ipj.tex
checkpoint

\subsection{BDOZ MAC Integrity}

@@

The integrity of values during protocol executions depends on the
partitioning $H,C$, since any value received from a member of
$C$ is initially considered to be low integrity. But as for
confidentiality types, we want our basic type analysis to be
generalizable to arbitrary $H,C$\cnote{Add related text to that
  section.}. So integrity type judgements are of the form
$\ipj{\eqs}{\prog}{\Delta}$, where $\eqs$ plays a similar role as in
confidentiality types, as a possibly weakened expression of algebraic
properties of $\prog$, and encironments $\Delta$ record integrity
information. Environments are ordered lists, since order of evaluation
is important for tracking integrity-- validating low
integrity information through MAC checking allows \emph{subsequent}
treatment of it as high integrity, but not \emph{before}.

The typing of protocols depends on a type judgement for expressions
of the form $\itj{\cid}{\be}{\ity{\cid}{V}}$, which records
messages and reveals $V$ used in the construction of $\be$.
In an assignment, this source is recorded in $\Delta$-- so for
example, for some string $w$ letting:
$$
\prog\ \defeq\ (\xassign{\mx{w}{1}}{\secret{w} - \flip{w}}{2};\ \rvl{w} := \mx{w}{1})
$$
the following judgement is valid:
$$
\ipj{\toeq{\prog}}{\prog}{(\mx{w}{1} : \ity{2}{\varnothing}; \rvl{w} : \ity{1}{\mx{w}{1}})}
$$
More formally, we defined validity as follows:
\begin{definition}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$, 
  we say $\ipj{\eqs}{\prog}{\Delta}$ is \emph{valid}
  iff it is derivable and $\eqspre \wedge \toeq{\prog} \models E$.
\end{definition}

In the above example, note that environment implicitly records
that $\rvl{w}$ depends on data from client 1, which in turn
depends on data from client 2. The rule for MAC
checking allows an overwrite of the dependency. We explore
the application of this in more detail in Section
\ref{section-examples}.

@@

In all cases, we want to determine the integrity level of computed
values based on assumed partitionins $H,C$. In the previous example,
we want to say that $\rvl{w}$ has low integrity if either client 1 or
2 is corrupt.  To this end we define \emph{security labelings}
$\seclev$ which are mappings from variables $x$ to security levels
$\latel$. By default, given a partitioning $H,C$ this labeling maps
messages to the integrity level of the owner.
\begin{definition}  
  Given $H,C$,
  define $\seclev_{H,C}$ such that $\seclev_{H,C}(\mx{w}{\cid} ) = \hilab$
  if $\cid \in H$  and $\lolab$
  otherwise for all $\mx{w}{\cid}$.
\end{definition}
During execution of a protocol, the integrity of messages and reveals
affected by values sent by other parties, as recorded in $\Delta$
obtained from its typing. We additionally need to determine
whether this impacts integrity, which we accomplish through
the inductively defined rewrite relation $\cheatj{\Delta}{H,C}{\seclev}$,
axiomatized in Figure \ref{fig-cheatj}.

>>>>

@@

The integrity of values during protocol executions depends on the
partitioning $H,C$, since any value received from a member of $C$ is
initially considered to be low integrity. But as for confidentiality
types, we want our basic type analysis to be generalizable to
arbitrary $H,C$. So integrity type judgements are of the form
$\ipj{\eqs}{\prog}{\Delta}$, where $\eqs$ plays a similar role as in
confidentiality types, as a possibly weakened expression of algebraic
properties of $\prog$, and encironments $\Delta$ record integrity
information. Environments are ordered lists, since order of evaluation
is important for tracking integrity-- validating low integrity
information through MAC checking allows \emph{subsequent} treatment of
it as high integrity, but not \emph{before}. Note that MAC checking is
\emph{not} a form of endorsement as it is usually defined (as a dual
of declassification \cite{sabelfeld2009declassification}), since a
successful check guarantees no deviation from the protocol.

The typing of protocols depends on a type judgement for expressions
of the form $\itj{\cid}{\be}{\ity{\cid}{V}}$, which records
messages and reveals $V$ used in the construction of $\be$.
In an assignment, this source is recorded in $\Delta$-- so for
example, for some string $w$ letting:
$$
\prog\ \defeq\ (\xassign{\mx{w}{1}}{\secret{w} - \flip{w}}{2};\ \rvl{w} := \mx{w}{1})
$$
the following judgement is valid:
$$
\ipj{\toeq{\prog}}{\prog}{(\mx{w}{1} : \ity{2}{\varnothing}; \rvl{w} : \ity{1}{\mx{w}{1}})}
$$
More formally, we define validity as follows:
\begin{definition}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$, 
  we say $\ipj{\eqs}{\prog}{\Delta}$ is \emph{valid}
  iff it is derivable and $\eqspre \wedge \toeq{\prog} \models E$.
\end{definition}

In the above example, note that the environment implicitly records
that $\rvl{w}$ depends on data from client 1, which in turn
depends on data from client 2. The rule for MAC
checking allows an overwrite of the dependency. We explore
the application of this in more detail in Section
\ref{section-examples}.

@@

In all cases, we want to determine the integrity level of computed
values based on assumed partitionins $H,C$. In the previous example,
we want to say that $\rvl{w}$ has low integrity if either client 1 or
2 is corrupt.  To this end we define \emph{security labelings}
$\seclev$ which are mappings from variables $x$ to security levels
$\latel$. By default, given a partitioning $H,C$ this labeling maps
messages to the integrity level of the owner.
\begin{definition}  
  Given $H,C$,
  define $\seclev_{H,C}$ such that $\seclev_{H,C}(\mx{w}{\cid} ) = \hilab$
  if $\cid \in H$  and $\lolab$
  otherwise for all $\mx{w}{\cid}$.
\end{definition}
But the values of messages and reveals may be
affected by values sent by other parties, which is
recorded in the $\Delta$ obtained from its typing. To determine
whether this impacts integrity for any given $H,C$, we apply
the inductively defined rewrite relation $\cheatj{\Delta}{H,C}{\seclev}$,
axiomatized in Figure \ref{fig-cheatj}. The composition
of typing and this latter rewriting obtains essentially
a traditional taint analysis, modulo MAC checking.
